VM-Centric Snapshot Deduplication\\ for Cloud Data Backup

### 2015-03-14 snapshot_system/mass_intro.tex
re

The main contribution of this paper is
1) a design and implementation of a backup service 
to integrate the VM-centric techniques while minimizing the resource impact on other 
collocated cloud services;
2) a VM-centric file block management to improve snapshot availability by
separating popular chunk replication and
packaging data chunks from the same VM into a file system block as much as possible; 
3) an analysis on the deduplication efficiency by using popular items
and also on the impact of above fault isolation design on snapshot availability.
The integrated optimization includes  similarity-guided local deduplication for
each VM to make the overall deduplication efficiency more competitive 
to a traditional deduplication scheme.
Our  experimental study compares  the VM-centric approach with the previous 
VM-oblivious approaches in terms of deduplication efficiency, resource usage,  and snapshot availability.
%Thus we improve  to avoid such VM-oblivious packaging.
%our approach uses a deduplication data chunk size that is smaller than a
%single file block and

>>>>

The main contribution of this paper is
1) a design and implementation of a backup service 
to integrate the VM-centric techniques while minimizing the resource impact on other 
collocated cloud services;
2) a VM-centric file block management to improve snapshot availability by
separating popular chunk replication and
packaging data chunks from the same VM into a file system block as much as possible; 
3) an analysis on the deduplication efficiency by using popular items
and also on snapshot availability improved by the above fault isolation design. 
The integrated optimization includes  similarity-guided local deduplication for
each VM to make the overall deduplication efficiency more competitive 
to a traditional deduplication scheme.
Our  experimental study compares  the VM-centric approach with the previous 
VM-oblivious approaches in terms of deduplication efficiency, resource usage,  and snapshot availability.
%Thus we improve  to avoid such VM-oblivious packaging.
%our approach uses a deduplication data chunk size that is smaller than a
%single file block and
